POODLE 1.0 - To the core of your data

### 2016-01-10 poodle_project/paper/main.tex
hoffe jetzt passt alles

SQLite \footnote{http://www.sqlite.org/} is the database system running in the background. We chose 
this software for several reasons. First, it is free of charge. Second, and more important SQLite is 
a small and fast database system written in C. So the requirement in space is very low. Since, the 
whole database is stored just in one file SQLite also has a incredibly good performance. Besides, 
SQLite guaranties that all transactions are ACID even if a system crash or power failure occurs. So 
we have a robust storage and access of data as well as a lot of functionality provided by the database 
system. In addition to the SQLite database POODLE's software creates a BLAST database for the provided 
data, too.

@@

POODLE web service is build with Vaadin \footnote{https://vaadin.com/home}. This allows a safe 
communication between the front end and the database layer as well as a smooth and easy handling of 
the side. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
service in the future. That could be necessary, if new functionalities are required. Currently, 
there are three pages with different roles. The search page provides a formula that can be used 
to perform a simple SQL search in the local database. Therefor, different files are displayed and 
can be filled by the user. A click on the search button will automatically build a SQL query and 
results are displayed, if there are available results. The new entry page allows to insert a new 
entry into the database. It also provide a Blast search against the NCBI databases to check, whether 
there are available information about the current sequence or not. Last but not least, users can 
perform a local Blast search against their one database or a remote Blast search against the NCBI 
databases on the Blast page.

@@

Our software package provides not just a database functionality for powerful and secure data storage 
and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search.

@@

\bibitem[Prli\'{c} {\it et~al}., 2012]{Prlic01}
Prli\'{c}, A., Yates, A., Bliven, S. E., Rose, P. W., Jacobsen, J., Troshin, P. V., ... Willis, S. (2012) BioJava: an open-source framework for bioinformatics in 2012. {\it Bioinformatics}, {\bf 28(20)}, 2693-2695. http://doi.org/10.1093/bioinformatics/bts494

>>>>

SQLite\footnote{http://www.sqlite.org/} is the database system running in the background. We chose 
this software for several reasons. First, it is free of charge. Second, and more important SQLite is 
a small and fast database system written in C. So the requirement in space is very low. Since, the 
whole database is stored just in one file SQLite also has a incredibly good performance. Besides, 
SQLite guaranties that all transactions are ACID even if a system crash or power failure occurs. So 
we have a robust storage and access of data as well as a lot of functionality provided by the database 
system. In addition to the SQLite database POODLE's software creates a BLAST database for the provided 
data, too.

@@

POODLE web service is build with Vaadin\footnote{https://vaadin.com/home}. This allows a safe 
communication between the front end and the database layer as well as a smooth and easy handling of 
the side. Since a website developed with Vaadin is highly modular, it is easy to extend the web 
service in the future. That could be necessary, if new functionalities are required. Currently, 
there are three pages with different roles. The search page provides a formula that can be used 
to perform a simple SQL search in the local database. Therefor, different files are displayed and 
can be filled by the user. A click on the search button will automatically build a SQL query and 
results are displayed, if there are available results. The new entry page allows to insert a new 
entry into the database. It also provide a Blast search against the NCBI databases to check, whether 
there are available information about the current sequence or not. Last but not least, users can 
perform a local Blast search against their one database or a remote Blast search against the NCBI 
databases on the Blast page.

@@

Our software package provides not just a database functionality for powerful and secure data storage 
and a easy-to-use interface but also a Blast (\citealp{Altschul01}) functionality. This functionality 
is implemented by a combination of Blast binaries provided by NCBI and the Biojava Api 
(\citealp{Prlic01}). There are two different Blast searches available in POODLE. On one hand, there 
is a remote Blast search on the NCBI server. And on the other hand, there is a local Blast search. 
The remote Blast search is not a fully functional copy of the NCBI web service but can used to 
perform a quick and simply search against NCBI databases, e.g. Swissprot (\citealp{Doni01}). But we do not recommend to 
overuse that because too many requests may cause a blacklisting by NCBI.

@@

\bibitem[Prli\'{c} {\it et~al}., 2012]{Prlic01}
Prli\'{c}, A., Yates, A., Bliven, S. E., Rose, P. W., Jacobsen, J., Troshin, P. V., ... Willis, S. (2012) BioJava: an open-source framework for bioinformatics in 2012. {\it Bioinformatics}, {\bf 28}(20), 2693-2695. http://doi.org/10.1093/bioinformatics/bts494

\bibitem[O'Donavan {\it et~al}., 2002]{Doni01}
O'Donovan, C., Martin, M.J., Gattiker, A., Gasteiger, E., Bairoch, A., Apweiler, R. (2002) High-quality protein knowledge resource: SWISS-PROT and TrEMBL {\it Brief. Bioinform.}  {\bf 3} (3), 275-284. doi: 10.1093/bib/3.3.275
